Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-06-09 analysis/paper/paper.Rmd
edit the site location
Added raw data (Dates) and created a new plot for temporal pattern

# combine site map and inset map
library(cowplot)
ggdraw() +
  draw_plot(map_of_sites) +
  draw_plot(plot = worldplot,
            x = 0.6, # x location of inset placement
            y = -0.09, # y location of inset placement
            width = .4, # Inset width
            height = .35, # Inset height
            scale = 0.5 # Inset scale
  ) +
  theme(panel.background = element_rect(fill='white', colour="white"),
        plot.background = element_rect(fill='white', colour="white"))

@@

### create column for "n = xx "
tcsa_raw <- tcsa %>% 
  group_by(raw_materials_top) %>% 
  add_tally() %>% 
  filter(n>1) %>% 
  mutate(label_raw = as.factor(paste0(raw_materials_top,' (n = ', n, ")"))) %>%   
  select(min_tcsa,
         raw_materials_top, 
       label_raw,
       n)   %>% 
  distinct_all()

tcsa_site <- tcsa %>% 
  group_by(site_name_top) %>% 
  add_tally() %>% 
  filter(n>1) %>% 
  mutate(label_site = as.factor(paste0(site_name_top,' (n = ', n, ")"))) %>%   
  select(min_tcsa,
         site_name_top, 
         label_site,
         n) %>% 
  distinct_all()
```

@@

```{r, raw-materials, fig.width= 4.5, fig.height=4, fig.cap="Histograms of TCSA values by lithic raw material."}
# Facet by raw materials
 ggplot(tcsa_raw,
              aes(min_tcsa, 
                  fill = n)) +
  geom_histogram() +
  theme_bw(base_size = 6) +
  labs(x = "TCSA", 
       y = "Count of artefacts") +
  facet_wrap(~label_raw,
                  scales = "free_y",
                  ncol = 1)  +
  scale_fill_viridis_c(name = "Number\nof artefacts")

@@

>>>>

# combine site map and inset map
library(cowplot)
ggdraw() +
  draw_plot(map_of_sites) +
  draw_plot(plot = worldplot,
            x = 0.43, # x location of inset placement
            y = -0.03, # y location of inset placement
            width = .4, # Inset width
            height = .35, # Inset height
            scale = 0.5 # Inset scale
  ) +
  theme(panel.background = element_rect(fill='white', colour="white"),
        plot.background = element_rect(fill='white', colour="white"))

@@

### create column for "n = xx "
tcsa_raw <- tcsa %>% 
  group_by(raw_materials_top) %>% 
  add_tally() %>% 
  filter(n>1) %>% 
  mutate(label_raw = as.factor(paste0(raw_materials_top,' (n = ', n, ")"))) %>%   
  dplyr::select(min_tcsa,
         raw_materials_top, 
       label_raw,
       n) %>% 
  distinct_all()

tcsa_site <- tcsa %>% 
  group_by(site_name_top) %>% 
  add_tally() %>% 
  filter(n>1) %>% 
  mutate(label_site = as.factor(paste0(site_name_top,' (n = ', n, ")"))) %>%   
  dplyr::select(min_tcsa,
         site_name_top, 
         label_site,
         n) %>% 
  distinct_all()
```

@@

```{r, raw-materials, fig.width= 4.5, fig.height=4, fig.cap="Histograms of TCSA values by lithic raw material."}
# Facet by raw materials
 ggplot(tcsa_raw,
              aes(min_tcsa, 
                  fill = n)) +
  geom_histogram() +
  theme_bw(base_size = 6) +
  labs(x = "TCSA", 
       y = "Count of artefacts") +
  facet_wrap(~label_raw,
                  scales = "free_y",
                  ncol = 1)  +
  scale_fill_viridis_c(name = "Number\nof artefacts") +
  annotate("rect", 
           xmin = 4,
           xmax = 18,
           ymin = 0,
           ymax = 2.5,
           fill = "green",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Poisoned\narrowheads",
               hjust = 0,
           y = (0+2.5)/2,
           x = 5.5) +
      annotate("rect", 
           xmin = 13,
           xmax = 55,
           ymin = 2.5,
           ymax = 5,
           fill = "blue",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Arrowheads",
               hjust = 0,
           y = (2.5+5)/2,
           x = 28) +
      annotate("rect", 
           xmin = 40,
           xmax = 76,
           ymin = 5,
           ymax = 7.5,
           fill = "orange",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Dart tips",
               hjust = 0,
           y = (5+7.5)/2,
           x = 53) +
      annotate("rect", 
           xmin = 44,
           xmax = 98,
           ymin = 7.5,
           ymax = 10,
           fill = "purple",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Javelin",
               hjust = 0,
           y = (7.5+10)/2,
           x = 70) +
     annotate("rect", 
           xmin = 88,
           xmax = 230,
           ymin = 10,
           ymax = 12.5,
           fill = "yellow",
           alpha = 0.2) +
      annotate("text", 
               label = "Thrusting spear",
               size = point_function_group_label_size,
               hjust = 0,
           y = (10+12.5)/2,
           x = 160)

@@

## Adding Radiocarbon dates info to the SP variation
```{r}
# radiocarbon data per assemblage
sitedate <- read_excel(here("analysis/data/raw_data/TCSA_site_info.xlsx"))

mydata_ages <-
  sitedate %>%
  separate(Period, into = c('age', 'error'),
           sep = "±") %>%
  mutate(age_ka = parse_number(age) / 1000,
         error = parse_number(error))

# combine the assemblage with age data

tcsa_site_ass <- tcsa %>% 
  left_join(mydata_ages) %>% 
  group_by(Assemblage) %>% 
 drop_na(age_ka) %>% 
  add_tally() %>% 
  mutate(label_site = as.factor(paste0(Assemblage,' (n = ', n, '), (', {round(age_ka,1)}, 'ka)' ))) %>%   
  dplyr::select(age_ka,
         min_tcsa,
         Assemblage, 
         label_site,
         n) %>% 
    distinct_all()

 ggplot(tcsa_site_ass,
              # aes(reorder(min_tcsa, -age_ka), 
               aes(min_tcsa,
                  fill = n)) +
  geom_histogram() +
  theme_bw(base_size = 6) +
  labs(x = "TCSA", 
       y = "Count of artefacts") +
  facet_wrap(~label_site,
                 scales = "free_y",
                  ncol = 1) +
    scale_fill_viridis_c(name = "Number\nof artefacts")
